%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Scientist} % Job title
    {Freelance} % Organization
    {Remote} % Location
    {May 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Developed software to collect HQ Trivia phone app data}. Created metrics and performed statistical modeling for game company. Insights helped build understanding of new market. (R,Python,SQL)}
        \item {\textbf{Data contributor to the Washington Post, The Wall Street Journal, and Money} using data and insights I collected from the HQ Trivia app. Recommended visualizations and uses of the data for their stories. (R, SQL)}
        \item {\textbf{Developed unsupervised model for outlier detection} and root cause analysis on server logs for major telecommunications company reducing manual work. (R, SQL)}
        \item {\textbf{Created sales forecast system for smarter inventory management} for power-sports retailer. Allowed company to better manage inventory to save storage costs and understand seasonal trends for efficient staffing. (Python)}
        \item {\textbf{Built data warehouse and implemented tableau server} for healthcare analytics company, perform ongoing maintenance and administration of data visualization servers and ETL. Work with clients to train and enable self-serve analytics. (Python, Tableau, SQL, Azure)}
        \item {\textbf{Technical Expert and Mentor for data science boot-camp company}. Mentor and lead students to learn and apply data science techniques as they work through curriculum. (Python, SQL, Spark)}  
        \item {\textbf{Georgia Tech graduate teaching assistant} for data analytics in business class. Helped answer questions, conduct office hours, and develop exams and test questions. (R)} 
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Scientist} % Job title
    {Ria Financial/Xe.com} % Organization
    {Denver, Co} % Location
    {Mar. 2017 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Developed classification models to identify chargeback orders} with high probability of winning. Reduced manual work by 70\% and increased overall dollar savings by 15\% annually. (Python, R, SQL, C\#)}
        \item {\textbf{Automated process of identifying early release customers with classification models.} Saved 2000 hours of manual work annually allowing fraud analysts to use their time more effectively. (R, SQL)}
        \item {\textbf{Created software and database to collect external data for customer profile modeling} data was used in more accurate risk rule creation and inferential models which ultimately reduced review rates and fraud detection false positives. (Python, SQL)}
        \item {\textbf{Developed entropy index to help identify customer account takeovers}. Reduced false positives by 50\% (R, SQL)}
        \item {\textbf{Designed and developed fraud dashboards} to automate reports, communicate fraud impacts, and alert management of outliers. Automation saved ~200 hours of manual report creation work annually. (Tableau, SQL, AWS)}
        \item {\textbf{Churn modeling and prediction} to identify customers for email win back campaigns. (Python, SQL)}
        \item {\textbf{Modeled customer order behavior and pricing} to determine when product pricing should change and for what corridors for maximum profit or customer acquisition. Implemented in internal web app for operations department. (R, SQL, AWS)}
        \item {\textbf{Fraud Analyst Lead}. Lead five fraud analysts to more effectively detect fraud using data and help build technical skills. Resulted in automating away reports, enabled self served data collection and increased win rates. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Business Intelligence Developer/Analyst} % Job title
    {Ria Financial} % Organization
    {Denver, Co} % Location
    {Dec. 2015 - Mar. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Transitioned company to Tableau for all reporting and metrics}. Responsible for the design, architecture, and administrator of Tableau for the digital business. Report automation saved over ~500 hours of manual work annually. (Tableau, SQL)}
        \item {\textbf{Data warehouse development}. Developed stored procedures, data models and Integrated external APIs into database for digital business. (SQL, AWS)}
        \item {\textbf{Customer lifetime value modeling and segmentation}. Operations used these findings for promotional spend amounts, business expansion decisions, and customer profiles. (R, SQL)}
        \item {\textbf{Developed clustering model to segment customers} based on purchasing habits, geography, and behavior. Marketing used results for email campaigns. (R, SQL)}
        \item {\textbf{Integrated Omniture visit, Apple reporting and order data} and created customer lifetime value by acquisition method (R,SQL)}
        \item {\textbf{On-boarding and training of new analysts}. Assisted on-boarding new marketing analysts and encourage data self sufficiency.}        
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Business Operations Analyst I-II} % Job title
    {DISH Network} % Organization
    {Denver, Co} % Location
    {Mar. 2013 - Dec. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Created simulation models of agent troubleshooting skills} to determine agent call flows and subject matter. (R, SQL)}
        \item {\textbf{Development of agent tech skill index}. Innovation quantified costs of each call subject to the agent level. Used in needs based training pilot and optimized call routing. (SQL, Tableau)}
        \item {\textbf{Implement needs based training pilot}. Selected to live in Philippines to carry out pilot, provide data analysis and help improve call center KPIs. (R, SQL, Tableau)}
        \item {\textbf{Developed ETL process} combining call data, agent troubleshooting data and operational cost data to quantify call subject costs to the minute. Allowed more intelligent call routing to agents with the highest efficiency for specific call subjects. Resulted in operational savings of 4 million dollars annually. (R, SQL)}
        \item {\textbf{Developed inferential statistical models} which helped build understanding around call center KPIs and agent promotion criteria. Communicated findings to DISH call center managers across the globe. (R, SQL, Tableau)}
        \item {\textbf{Reporting on technical service outages}. Shared reports to executives across the organization to understand impact. (SQL, Tableau)}
      \end{cvitems}
    }

\end{cventries}
