%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead Developer and Data Scientist} % Affiliation/role
    {HQ Insiders (HQinsiders.com)} % Organization/group
    {} % Location
    {Dec. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed software to collect data from HQ Trivia phone app, only known database on metrics from game.}
        \item {Launched hqinsider.com website to share findings.}        
        \item {Performed inferential statistics on data which have been used by businesses and media organizations.}
        \item {Provide data visualization recommendations to media outlets and development of data visualization for presentations. }        
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Student} % Affiliation/role
    {Textual Analysis of Reddit to Predict Future Stock Returns} % Organization/group
    {} % Location
    {2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Collected and modeled data to understand the impact of social media posts on the future prices of individual stocks.}
        \item {Integrated reddit.com data and stock market data to be used in modeling.}
        \item {Conducted various experiments to determine the best sentiment analysis technique on reddit.com data.}
        \item {Experiments with various regression models and time periods to predict future stock returns.}
        \item {Assisted in development of web application to display real time sentiment analysis and individual stock prediction based on experiment results.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
